### 2020-06-09 sections/major/major.tex
Reshuffled stochasticity and fragments sections

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}

\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
\end{proof}

@@

\subsection{General resource fragments}\label{sec:frag}

Subdividing magic into $\sigma$-fragments
Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, 
\begin{equation}\label{eq:monotonicity}
    \cal{M}(\rho_1) \leq \cal{M}(\rho_2)\ \text{if}\ \rho_1 \prec_{\R} \rho_2,
\end{equation}
reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}

\begin{figure}
    \centering
    \includegraphics[height=3cm]{sections/major/fragments.pdf}
    \caption{Fragments \nick{Split into subfigures}
    }
    \label{fig:fragments}
\end{figure}

Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ \nick{actually it maps all states, not just the free ones} and $\rho_1 \prec_{\R} \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ for any states $\rho_1, \rho_2$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
Fragment $\R'$ is the image of the projection $\Pi$.
Considering a resource projection is particularly useful when the structure of the fragment is more tractable.

\begin{proposition}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
\end{proposition}
\begin{proof}
    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

\begin{proposition}
    Every theory of magic $\R = (\F, \O)$ is a fragment of the maximal theory $\Rmax$.
\end{proposition}
\begin{proof}
    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
    \begin{equation}
    \Pis(\sigma) =
    \begin{cases}
        \sigma,\ &\sigma \in \F, \\
        \frac{1}{d}\id,\ &\sigma \notin \F.
    \end{cases}
    \end{equation}
    \nick{Perhaps $\Pis = $ identity}
    Let $1_{\rm{C}}$ denote the identity channel.
    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

Monotones reduce the structure of the theory into a real number ordering, therefore a monotone is the simplest tractable projection as formally stated in~\cref{thm:monofrag}.
\begin{proposition}\label{thm:monofrag}
	Let $\cal{M}$ be a monotone defined in the context of a resource theory $\R$. 
	Then $\cal{M}$ is a resource projection that  reduces the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Consider a monotone $\cal{M}$ in the context of a general resource theory $\R = (\F, \O)$.
	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$. 
	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.

	The defining property of a monotone, given in~\cref{eq:monotonicity} ensures condition 1 of~\cref{def:fragment}.

	We can then project any $\E \in \O$ onto a function $f \in \O'$, so that $f$ maps $\cal{M}(\rho)$ onto $\cal{M}(\E(\rho))$ for all states $\rho$.

	\nick{expand}
\end{proof}

@@

The zoo of all the operation classes is summarised in ~\cref{fig:zoo}.
Completely positive-Wigner-preserving operations ($\cpwp$) form the largest operation class in the literature.
Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
For example, the stabilizer-preserving ($\spo$)~\cite{cit:ahmadi} and completely stabilizer-preserving ($\cspo$)~\cite{cit:seddon} operation subclasses follow the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$ and therefore are described by our $\sigma$-fragments.

\begin{figure}[b]
    \centering
        \includegraphics[scale=0.45]{sections/major/operations.pdf}
    \caption{Zoo of allowed operations for magic resource theories.
    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$.
    We introduce fragments $\O_\sigma \subset \stochw,\ \sigma \in \F$ that cover $\cpwp$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
    \nick{fragments are the intersections of blue and orange, not the whole bubble - technically $\stochw$ should be replaced by its operational pre-image.}
    }
    \label{fig:zoo}
\end{figure}

>>>>

Let $\R = (\F, \O)$ be a general resource theory.
We call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}

\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
\end{proof}
Therefore, identifying an invariance in the setup helps in determining whether a state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
If state $\sigma$ is left invariant by an operational sequence, then the total operation $\E$ that converts $\rho$ to $\tau$ lies in $\O_\sigma$. \nick{expand}

The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
In particular, the stabilizer operations $\so$ are contained within $\Omax$.
\begin{figure}[t]
    \centering
        \includegraphics[scale=0.47
        ]{sections/major/operations.pdf}
    \caption{Zoo of allowed operations for magic resource theories.
    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
    We introduce fragments $\O_\sigma,\ \sigma \in \F$ that cover $\Omax$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
    }
    \label{fig:zoo}
\end{figure}

@@

@@
